A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-12-06 doc/review-acom/response-to-referees.tex

The original procedure was designed to test whether a root was
an eigenvalue in a manner independent of the interpolant we had
computed for the Fredholm determinant. Thus, we checked the several smallest
singular values to see if any eigenspaces of dimension larger
than one were associated
with the weird double roots. None were found. We thus chose what
seemed to be the better root in an ad hoc way. As noted above, this
procedure is no longer necessary when calling \texttt{roots} with
the subdivision procedure suppressed.

\item[7.] {\color{blue}In the caption of figure 5 the given interval for $k$
  does not match with the plots. Moreover, in each plot of figure
  5 two functions are given but in the caption only one function is described.}

\item[8.] {\color{blue}Subsection 1.1 (”Relation to other work“) may
  lead to the false impression that boundary integral equations of the
  second kind combined with the proposed root finding method is the only
  profound and reasonable boundary integral equation approach for the Stokes
  eigenvalue problem. The authors seem not be aware of works which deal with
  boundary integral equation methods based on integral equations of the
  first kind (for several types of eigenvalue problems(Laplacian, Maxwell,
  fluid-solid interaction, plasmonics, ....)) which are well analyzed and for
  which a rigorous and comprehensive convergence theory is established.
  Such kind of an approach could be also applied to the Stokes eigen-
  value problem. Moreover, in these works instead of the root search for
  the determinant the contour integral method for nonlinear eigenvalue
  problem is used for which multiple and spurious eigenvalues seem not
  to be a problematic issue. In some way these alternatives should be
  briefly mentioned in the paper.}

  This comment is well taken.
  We did not mean to give this impression but had intended this section
  to be focused on methods specifically for the Stokes eigenvalue problem.
  We have added some references to applications treated using integral
  equation methods in the literature and reworked the section
  a little.

### 2019-12-07 doc/review-acom/response-to-referees.tex

\item[2.] {\color{blue}
  In the abstract the Stokes operator is denoted as fourth-order operator.
This is unusual and in my opinion not the case (even if there is an
equivalence to a forth-order operator).}

We see how this could be confusing and have adjusted this phrasing.

\item[3.] {\color{blue} I would appreciate it if the following issue would be addressed in the
paper: under which weaker conditions (not analytic boundary, non-
simple eigenvalues) convergence of the discretization of the eigenvalues
can be proven. (Are there results concerning the convergence of the
eigenfunctions?)}

The question of addressing this problem under weaker assumptions of smoothness of the boundary
is a very interesting one. To the best of our knowledge, this question hasn't even been addressed 
Laplace's equation.
We have a sketch of a proof for the eigenvalues and eigenfunctions
for the Laplace operator where we can show that the eigenvalues and eigenfunctions
converge at an algebraic rate (dependent on the smoothness of curves) for $C^{\ell}$, $\ell\geq 2$ boundaries.
The procedure of using the Fredholm determinant as stated does not work on Lipchitz boundaries, since
the corresponding operators are not second kind.

However, we feel that the discussion would be fairly technical and take away from the main results of 
the paper --- demonstrating the use of Fredholm determinants and second kind formulations for 
computing the Stokes eigenvalues and eigenfunctions.  For this reason we feel that this analysis should be carried out in a separate note for the use of Fredholm determinants for the computation of eigenvalues and eigenvectors of Laplace's and Stoke's equation.

We've included a sketch of the proof below.

The sketch of the proof goes as follows. The main estimate needed is to show that the error in
computing the Fredholm determinant at the eigenvalues of the Stokes operator is directly proportional
to the quadrature error applied to the null vector of the second kind Fredholm equation. 
Based on Fredholmness of the operator from $C^{m,\alpha} \to C^{m,\alpha}$ for some $m<\ell$ and $\alpha>0$, 
when the boundary is $C^{\ell}$, one can show that the resulting null vector must be at least in $C^{m,\alpha}$.
The quadrature error using Kress quadratures converges algebraically when both the boundary and density being
approximated are $C^{m,\alpha}$.

@@

\item[6.] {\color{blue}
  For me it is not clear why with the suggested procedure spurious ``double roots''
  may be detected. What is actually the argument that this
  procedure detects spurious double roots?}

The original procedure was designed to test whether a root was
an eigenvalue in a manner independent of the interpolant we had
computed for the Fredholm determinant. Thus, we checked the several smallest
singular values to see if any eigenspaces of dimension larger
than one were associated
with the weird double roots. None were found. We thus chose what
seemed to be the better root in an ad hoc way. As noted above, this
procedure is no longer necessary when calling \texttt{roots} with
the subdivision procedure suppressed.

\item[7.] {\color{blue}In the caption of figure 5 the given interval for $k$
  does not match with the plots. Moreover, in each plot of figure
  5 two functions are given but in the caption only one function is described.}

Apologies about that. The caption for figure 5 has now been fixed. The two curves
correspond to the real and the imaginary part of the Fredholm determinant.

### 2019-12-07 doc/review-acom/stokes-eig.tex
updating response to 3

\begin{figure}
\centering
\includegraphics[width=0.98\linewidth]{det_spur.pdf}
\caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
and $f_{D}^{N}(k)$ on the interval $k=[13,14]$ with $N=368$. The vertical
dotted line denotes the spurious eigenvalue $k_{0} = 14.79595178235126$ 
and $f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}|=6.8\times 10^{-12}$.
On the other hand $|f_{C}^{N}(k_{0})|=0.42$, and thus $\cI-2\cD_{k}-2i\cS_{k} 
-2\cW$ has no 
spurious eigenvalue in the neighborhood of $k=k_{0}$.}
\label{fig:spur}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.98\linewidth]{det_spur.pdf}
\caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
and $f_{D}^{N}(k)$ on the interval {\color{red} $k=[14,15]$} with $N=368$ 
{\color{red}(the 
solid lines are the real parts of the determinant and the dashed lines
are the imaginary parts of the determinant)}. The vertical
dotted line denotes the spurious eigenvalue $k_{0} = 14.79595178235126$ 
and $f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}|=6.8\times 10^{-12}$.
On the other hand $|f_{C}^{N}(k_{0})|=0.42$, and thus $\cI-2\cD_{k}-2i\cS_{k} 
-2\cW$ has no 
spurious eigenvalue in the neighborhood of $k=k_{0}$.}
\label{fig:spur}
\end{figure}
